---
title: "Tumo Day 6 Personal Geographies"
output: html_notebook
---

```{r}

library(rio)
library(tidyverse)

video_games_sales <- import("Video_Games_Sales.csv")

```

```{r}

# Viewing data structure

View(video_games_sales) 

ncol(video_games_sales)
nrow(video_games_sales)

```

```{r}

video_games_sales <- video_games_sales %>%
  group_by(Year_of_Release) %>%
  summarise(freq=n()) %>%
  mutate(prop=freq/sum(freq))

ggplot(video_games_sales, aes(x="", y=factor(Year_of_Release), fill=c(Year_of_Release))) +
  geom_bar(color="white", stat="identity", width=1) +
  coord_polar("y", start=0) +
  labs(title="Windows Games Sales For Each Platform",
       x=NULL,
       y=NULL,
       fill = "Platforms",
       caption = "Source: https://www.kaggle.com/rush4ratio/video-game-sales-with-ratings") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) 

```

```{r}

cor(x = video_games_sales$Year_of_Release, y=video_games_sales$Genre, method="pearson", use="pairwise.complete.obs")

video_games_sales %>%
  ggplot(mapping=aes(x=Year_of_Release, y=Genre)) +
  geom_point(color="purple") +
  geom_smooth(color="lightblue", se=FALSE, method="lm") +
  labs(title="Relationship Between Post-Graduation Income and Unemployment Rates \nIndectaes Negative Relationship",
       x="75th Percentile of Post-Graduatio Income",
       y="Unemployment Rate",
       caption = "https://github.com/fivethirtyeight/data/blob/msater/college-majors")

```

Null hypothesis:
  + p = 0
Alternate hypothesis:
  + $ p \ne0 $
Conduct a test:
  + I am going to use a hypothises test that leverages correlation to determine the realationship between the 75th percentile of post-graduation income and unemployement rate. I am choosing this test because I have two quantitative varibales, and I am curious about the strenght/direction of the relationship between them.

```{r}

# Hypothesis testing

cor.test(x=video_games_sales$P75th, y=video_games_sales$Unemployment_rate, method="pearson")

```

Draw a conclusion:

Based on the results of the test, we can reject the null hypothesis, which claims that the two variabels do not have a crrelation. Therefore, we can expect income to vary inversely with unemployment rate after graduation at a statistically significant level.